Cluster Difference Imaging Photometric Survey. I. Light Curves of Stars in Open Clusters from TESS Sectors 6 \& 7

### 2019-08-12 paper_I/ms.tex
improve discussion / conclusion
* add context w.r.t. other reduction efforts
* mv hyperparameter discussion out of methods, to discussion

% BEGIN NUMBERS
\newcommand{\numberpcs}{39\ }  % 2019/06/28 unanimous gold
\newcommand{\numberzaripcs}{10\ }  % 2019/06/28 unanimous gold
\newcommand{\numberclusterpcs}{29\ }  % 2019/06/28 unanimous gold
\newcommand{\sVInumberlcs}{67{,}612\ }  % 2019/07/27 not allnan
\newcommand{\sVIInumberlcs}{91{,}731\ }  % 2019/07/27 not allnan
\newcommand{\numberlcs}{159{,}343\ } % 2019/06/20 sum
\newcommand{\numberclusters}{596\ } % 2019/07/01 paper_plot_all_figures.py
\newcommand{\pctoflcswithage}{77} %  2019/07/02 from hist_logt.png

@@

The Transiting Exoplanet Survey Satellite (TESS,
\citealt{ricker_transiting_2015}) holds the promise to deliver the
most homogeneous and comprehensive cluster photometric survey in
history.  Based on the cluster membership data of
\citet{Kharchenko_et_al_2013}, approximately $2\times10^5$ open
cluster members brighter than $T=16$ will be observed in the
full-frame images over the first two years of TESS observations.  This
count includes the ``most probable'' members, which by the
\citet{kharchenko_global_2012} definition requires the independent
kinematic, photometric, and spatial membership probabilities to each
exceed 61\%.  The actual number of stars in clusters is larger, as the
membership catalogs are not yet complete, even at these relatively
bright magnitudes \citep[{\it
e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019,kounkel_untangling_2019,sim_open_2019}.

@@

One way to quantify the blending problem is to determine what fraction
of the total flux in a photometric aperture is contributed by a
particular target star. Aperture photometry is reliable when this
fraction is close to unity.  Difference imaging
\citep{Alard_Lupton_1998,miller_optimal_2008}, in our group's
experience, can be viable down to crowding fractions of 10\%.  Based
on the \citet{Kharchenko_et_al_2013} cluster membership data, and the
density of background stars, we calculated that the median dilution
fraction is 0.13, for cluster stars with $T< 16$ and an aperture
radius of 2 pixels.  Thus, for at least $\sim$$10^5$ cluster stars,
difference imaging may be advantageous.

@@

We have therefore begun to apply difference imaging to the TESS
images, with a focus on any star that could be a member of a group.
We are also including some stars that we suspect are young due to
combined photometric and astrometric indicators.  A major motivation
for this effort is to discover giant transiting planets with known
ages.  The focus of the present study however is to describe our
methods, and to produce a general-purpose dataset applicable for
studies both in exoplanetary and also stellar astrophysics.

@@

\subsection{Choice of convolution kernel}

@@

However, we caution that within these fine-tuning experiments, we
found that transit signals near the noise floor could fall under the
noise floor for different cases of tuned parameters.  In the longer
term, developing an image-subtraction method that marginalizes over
uncertainties of how to chose ``optimal'' kernels would be desirable.
Pixel-level image subtraction methods that omit these parameters
entirely are similarly worth exploring \citep{wang_pixel-level_2017}.

With a kernel selected, and the convolution and subtraction performed,
we calculate the instrumental fluxes for each frame per
Equation~\ref{eq:ism_flux_measurement}.  We did this with three
different aperture sizes: for this work, circles of radii 1 pixel, 1.5
pixels, and 2.25 pixels.  These sizes were chosen to roughly span the
range of optimal aperture sizes reported by
\citet{Sullivan_et_al_2015}.  Finally, to convert from a list of flux
measurements for each source on a frame to light curves, we used the
\texttt{fitsh} transposition tool \texttt{grcollect}.

@@

A point worth re-emphasizing is that the stars in the sample must be
understood to be {\it candidate} cluster stars, and the possibility of
photometric blends is important to rule out in subsequent vetting
efforts of any variable object.  Careful understanding of the cluster
itself is also important, as some clusters are less certain to exist
than others \citep[{\it e.g.}, the infra-red clusters identified
by][]{froebrich_FSR_2007}.

We remind the reader that our goal in creating our target catalog was
completeness, rather than reliability.  To create clean sub-samples,
we advise using the \texttt{CDEXTCAT} header keyword available in the
FITS files, which can be used to merge against the original source
catalog to obtain the membership probabilities claimed by the original
catalog.  Alternatively, simply restricting the targets of interest to
those with provenance from {\it e.g.}, the Gaia-DR2 data is another
way to produce a cleaner sample of cluster targets.

Despite our goal of completeness, some clusters may still be missing
members~--~the census of nearby coeval stellar populations is still
very much in flux. For instance, during the preparation of this work,
\citet{sim_open_2019} identified 209 new open cluster candidates
within 1~kpc through visual inspection of Gaia-DR2 data.  Similarly,
\citet{kounkel_untangling_2019} searched for groups near the galactic
plane within 1~kpc, and along with the known clusters found hundreds
of new ``strings'' of kinematically associated stars, which could be
coeval.

Another area in which we may be incomplete is in sub-clusters of
broader star-forming complexes. One important example is the Orion
Nebula (M42; NGC 1976).  While it was observed by TESS in Sector~6,
searching our light curves for stars within 40 arcminutes and 100
parsecs of the Orion Nebula's center yielded only 180 light curves,
with 85 labelled members.  The Orion Nebula has far more known members
\citep{jones_proper_1988}.  However, due to a combination of the
spatially distributed nature of the broader complex, as well as
differential extinction, the automated methods of the
\citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014} assigned
the Orion Nebula only 44 and 326 members, respectively.
\citet{cantat-gaudin_gaia_2018} explicitly excluded young star-forming
regions from their search, since the underlying assumption of their
clustering method (uniformity in the field star distribution) breaks
down in highly clustered star-forming regions.

These concerns will likely drive us to expand beyond the current
sample of target stars in future work.  For the time being though, the
light curves exist and are amenable for astrophysical studies.  We
invite any who wish to explore the time evolution of stellar or
exoplanetary systems to interact with the data at \stscilink.

\acknowledgements
L.G.B.\ acknowledges helpful discussions with 
T.~Cantat-Gaudin,
C.~Huang,
and M.~Soares-Furtado.  The authors are also
grateful to the many people who have turned TESS from an idea into
reality.
%
Coauthors thank ... %FIXME
%
L.G.B. and J.H. acknowledge support by the TESS GI Program, program
G011103, through NASA grant 80NSSC19K0386.
%
G.B. acknowledges support through NASA grant NNG14FC03C.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
The Digitized Sky Surveys were produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166. The images of these
surveys are based on photographic data obtained using the Oschin
Schmidt Telescope on Palomar Mountain and the UK Schmidt Telescope.
The plates were processed into the present compressed digital form
with the permission of these institutions.
%
\newline
%
\facility{
	2MASS \citep{skrutskie_tmass_2006},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018},
	TESS \citep{ricker_transiting_2015},
	UCAC4 \citep{zacharias_fourth_2013}
    %DSS (CITE)    
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{astroquery.gaia} CITE,
  %\texttt{astroquery.simbad} CITE,
  %\texttt{astroquery.mast} CITE,
  %\texttt{astroquery.nasaexopanetarchive} CITE,
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{fitsh} \citep{Pal_2012},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122}
  \texttt{psycopg2} (\url{initd.org/psycopg})
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{scikit-learn} \citep{sklearn_2011},
  \texttt{TagSpaces} (\url{tagspaces.org}),
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
  \texttt{VARTOOLS} \citep{Hartman_Bakos_2016}
  \texttt{wotan} \citep{hippke_wotan_2019},
}

>>>>

% BEGIN NUMBERS
\newcommand{\numberpcs}{24\ }  % 2019/08/12 gold post-vet
\newcommand{\numberzaripcs}{10\ }  % 2019/06/28 unanimous gold
\newcommand{\numberclusterpcs}{29\ }  % 2019/06/28 unanimous gold
\newcommand{\sVInumberlcs}{67{,}612\ }  % 2019/07/27 not allnan
\newcommand{\sVIInumberlcs}{91{,}731\ }  % 2019/07/27 not allnan
\newcommand{\numberlcs}{159{,}343\ } % 2019/06/20 sum
\newcommand{\numberclusters}{596\ } % 2019/07/01 paper_plot_all_figures.py
\newcommand{\pctoflcswithage}{77} %  2019/07/02 from hist_logt.png

@@

The Transiting Exoplanet Survey Satellite (TESS,
\citealt{ricker_transiting_2015}) holds the promise to deliver the
most homogeneous and comprehensive cluster photometric survey in
history.  Based on the cluster membership data of
\citet{Kharchenko_et_al_2013}, approximately $2\times10^5$ open
cluster members brighter than $T=16$ will be observed in the
full-frame images (FFIs) over the first two years of TESS
observations.  This count includes the ``most probable'' members,
which by the \citet{kharchenko_global_2012} definition requires the
independent kinematic, photometric, and spatial membership
probabilities to each exceed 61\%.  The actual number of stars in
clusters is larger, as the membership catalogs are not yet complete,
even at these relatively bright magnitudes \citep[{\it
e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019,kounkel_untangling_2019,sim_open_2019}.

@@

One way to quantify the blending problem is to determine what fraction
of the total flux in a photometric aperture is contributed by a
particular target star. Aperture photometry is reliable when this
fraction is close to unity.  Difference imaging
\citep{Alard_Lupton_1998,miller_optimal_2008}, in our group's
experience, can be viable down to crowding fractions of 10\%.  Based
on the \citet{Kharchenko_et_al_2013} cluster membership data and the
density of background stars, we calculated that the median dilution
fraction is 0.13, for cluster stars with $T< 16$ and an aperture
radius of 2 pixels.  Thus, for at least $\sim$$10^5$ cluster stars,
difference imaging may be advantageous.

@@

We have therefore begun to apply difference imaging to the TESS
FFIs, with a focus on any star that could be a member of a group.
We are also including some stars that we suspect are young due to
combined photometric and astrometric indicators.  A major motivation
for this effort is to discover giant transiting planets with known
ages.  The focus of the present study however is to describe our
methods, and to produce a general-purpose dataset applicable for
studies both in exoplanetary and also stellar astrophysics.

@@

\subsection{Choice of convolution kernel}
\label{subsec:tuneconvkernel}

@@

With a kernel selected, and the convolution and subtraction performed,
we calculated the instrumental fluxes for each frame per
Equation~\ref{eq:ism_flux_measurement}.  We did this with three
different aperture sizes: for this work, circles of radii 1 pixel, 1.5
pixels, and 2.25 pixels.  These sizes were chosen to roughly span the
range of optimal aperture sizes reported by
\citet{Sullivan_et_al_2015}.  Finally, to convert from a list of flux
measurements for each source on a frame to light curves, we used the
\texttt{fitsh} transposition tool \texttt{grcollect}.

@@

There are a number of other TESS data
processing efforts that we expect will complement our results.
These include the NASA Ames SPOC pipeline \citep{jenkins_spoc_2010}, the MIT
Quick-Look-Pipeline \citep{huang_tess_2018}, \texttt{eleanor}
\citep{feinstein_eleanor_2019}, the \citet{oelkers_precision_2018}
difference imaging pipeline, the TESS Asteroseismic Consortium (TASOC)
pipeline \citep{lund_k2p_2015,handberg_tess_2019}, and the Padova
team's effort (D{.} Nardiello, submitted; {\it e.g.},
\citealt{libralato_psf-based_2016}).

Most of these pipelines are geared towards tasks more general than our
own, and use aperture photometry.  The SPOC pipeline
produces the calibrated FFIs from raw images, processes 2 minute data,
identifies exoplanets, and produces the TESS data
products of record.  The MIT-QLP processes a subset of stars on the
FFIs, identifies exoplanets, and the affiliated TESS Science Office
alerts object of interest for ground and space-based followup.  The
\texttt{eleanor} pipeline is a user-friendly tool for
extracting light curves from the FFIs.  The team developing it is
also performing transit searches across the full set of FFIs.  The
TASOC pipeline is primarily aimed towards asteroseismology.  The
\citeauthor{oelkers_precision_2018} pipeline was aimed at broad,
all-sky variability searches, and used similar difference
imaging methods as our own.  Finally, the Padova team's effort is
developed with a similar focus towards clusters as our work, but uses
PSF subtraction to mitigate crowding.  This ecosystem
provides many opportunities for methodological improvements as light
curve products continue to be made public.

There are of course caveats and possible areas for improvement
in our own work.
One methodological point concerns the hyperparameter tuning
required by our difference imaging method (\S~\ref{subsec:tuneconvkernel}).
Within our fine-tuning experiments over different kernel box-sizes
and polynomial weightings,
we found that low-significance transit signals could be ``lost''
relative to the noise for different choices of parameters that
ideally would not affect the photometric pipeline's results.
In the longer
term, developing an image-subtraction method that marginalizes over
uncertainties of how to chose ``optimal'' kernels would be desirable.
Pixel-level image subtraction methods that omit these parameters
entirely are also worth exploring \citep{wang_pixel-level_2017}.

A separate point to re-emphasize is that stars in our sample must be
understood to be {\it candidate} cluster stars, and ruling out the possibility of
photometric blending is important in subsequent vetting
efforts of any variable object.  Careful understanding of the cluster
itself is also important, as some clusters are less certain to exist
than others \citep[{\it e.g.}, the infrared clusters identified
by][]{froebrich_FSR_2007}.

We remind the reader that our goal in creating our target catalog was
completeness, rather than reliability.  To create clean sub-samples,
we advise using the \texttt{CDEXTCAT} header keyword available in the
FITS files, which can be used to merge against the original source
catalog to obtain the membership probabilities claimed by the original
catalog.  Alternatively, simply restricting the targets of interest to
those with provenance from {\it e.g.}, the Gaia-DR2 data is another
way to produce a clean sample of cluster targets.

Despite our goal of completeness, some clusters still may be missing
members~--~the census of nearby coeval stellar populations is
very much in flux. For instance, during the preparation of this work,
\citet{sim_open_2019} identified 209 new open cluster candidates
within 1~kpc through visual inspection of Gaia-DR2 data.  Similarly,
\citet{kounkel_untangling_2019} searched for groups near the galactic
plane within 1~kpc, and along with known clusters found hundreds
of new ``strings'' of kinematically associated stars, which could be
coeval.

Another area in which we may be incomplete is in sub-clusters of
large star-forming complexes. One important example is the Orion
Nebula (M42; NGC 1976).  While it was observed by TESS in Sector~6,
searching our light curves for stars within 40 arcminutes and 100
parsecs of the Orion Nebula's center yielded only 180 light curves,
with 85 labelled members.  The Orion Nebula has far more known members
\citep{jones_proper_1988}.  However, due to a combination of the
spatially distributed nature of the broader complex, as well as
differential extinction, the automated methods of the
\citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014} assigned
the Orion Nebula only 44 and 326 members, respectively.
\citet{cantat-gaudin_gaia_2018} explicitly excluded young star-forming
regions from their search, since the underlying assumption of their
clustering method (uniformity in the field star distribution) breaks
down in highly clustered star-forming regions.

These concerns will likely drive us to expand beyond the current
sample of target stars in future work.  For the time being, the
light curves exist and are amenable for astrophysical studies.  We
invite any who wish to explore the time evolution of stellar or
exoplanetary systems to interact with the data at \stscilink.

\acknowledgements
L.G.B.\ acknowledges helpful discussions with 
T.~Cantat-Gaudin,
C.~Huang,
M.~Soares-Furtado,
J.~Wallace, and
S.~Yee.  The authors are also
grateful to the many people who have turned TESS from an idea into
reality.
%
L.G.B. and J.H. acknowledge support by the TESS GI Program, program
G011103, through NASA grant 80NSSC19K0386.
%
G.B. acknowledges support through NASA grant NNG14FC03C.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
The Digitized Sky Surveys were produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166. The images of these
surveys are based on photographic data obtained using the Oschin
Schmidt Telescope on Palomar Mountain and the UK Schmidt Telescope.
The plates were processed into the present compressed digital form
with the permission of these institutions.
%
\newline
%
\facility{
	2MASS \citep{skrutskie_tmass_2006},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018},
	TESS \citep{ricker_transiting_2015},
	UCAC4 \citep{zacharias_fourth_2013}
    %DSS (CITE)    
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{astroquery.gaia} CITE,
  %\texttt{astroquery.simbad} CITE,
  %\texttt{astroquery.mast} CITE,
  %\texttt{astroquery.nasaexopanetarchive} CITE,
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{fitsh} \citep{Pal_2012},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122}
  \texttt{psycopg2} (\url{initd.org/psycopg})
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{scikit-learn} \citep{sklearn_2011},
  \texttt{TagSpaces} (\url{tagspaces.org}),
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
  \texttt{VARTOOLS} \citep{Hartman_Bakos_2016}
  \texttt{wotan} \citep{hippke_wotan_2019},
}
